\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 learning.tex
changes
garbage stuff

\begin{example}
\mypara{\emph{Relationalize}}: For each cell $C$, perform regression analysis on
    the respective set of trajectory segments $D(C)$, and compute a
    set of affine relations $R_{C,C'}(\x,\x')$ between $\x \in C$ and $\x'
    \in C'$ s.t., $\text{edge} (C,C') \in \scr{H}(0.1)$. Annotate
    each edge in the graph $\scr{H}(0.1)$ with the respective
    relation.

    \figref{vdp-map} shows the cells and the trajectory segments, which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.  Finally, \figref{vdp-graph} and
    \tabref{vdp-pwa} show the enriched graph $G^R$ with its transition
    relations. Note that self loops result when an observed trajectory
    segment has its $start$ and $end$ states in the same cell.
\end{example}

>>>>

\begin{example}
    For the~\exref{vdp}, for every abstract relation between two cells
    $C, C'$, linear regression analysis is performed on the respective
    set of trajectory segments, and the affine relation is computed.
    \figref{vdp-abs-paths} shows the cells and the trajectory segments, which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.
\end{example}

### 2017-06-12 scam.tex
garbage stuff

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}{vdp-cont}
\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

@@

% \mypara{Abstract}: Assume an implicit abstraction using the quantization
%         function $\quant_{\epsilon=0.2}(\x)$. The corresponding reachability
%     graph is $\scr{H}(\Delta=0.1)$.
% 
% \mypara{Discover}: Using scatter-and-simulate, enumerate a finite number
%     of cells (vertices) and the relations (edges) of the graph
%     $\scr{H}(0.1)$. Associate the set of generated trajectory
%     segments with their respective originating cells using a map $\ds:C
%         \mapsto \setof{(\vx,\vx') |\vx \in C}$.

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%

>>>>

% \inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
% Pol: continuous trajectories. Red and green boxes indicate unsafe and
% initial sets.}{vdp-cont}
\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

@@

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\epsilon=0.2$. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

\begin{example}[Van der Pol Oscillator]~\label{ex:vdp}
We use the Van der Pol oscillator benchmark
from~\cite{zutshi2014multiple} to demonstrate our falsification
approach. We want to falsify property $P_3$, $x_{unsafe}\in[-1,
-6.5]$ and $y_{unsafe}\in[-0.7, -5.6]$, given the initial set
indicated $x0\in[-0.4, -0.4],\; y_0\in[0.4, 0.4]$. The abstraction
is defined by $\epsilon=0.2$, which results in an evenly gridded
state-space, where each cell is of size $0.2 \times 0.2$ units.
$ScatterAndSimulate$ is then used to construct the abstraction,
using $2$ samples per cell and the time step $\Delta = 0.1s$. The
result is plotted in ~\figref{vdp-abs}.
\end{example}

@@

\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{
Abstract trajectories discovered by $ScatterAndSimulate$. Each
    rectangle denotes a cell which is uniquely identified  by the
    tuple against it.
}{vdp-abs-paths}

Going back to the~\exref{vdp}, $ScatterAndSimulate$ is able to find
    several abstract trajectories as shown in~\figref{vdp-abs-paths}.
    However, typically, the refinement by increasing the quantization
    precision requires $4$ refinement iterations and finally finds a
    concrete counter-example for $\epsilon=0.125$.

\end{example}
